fdcoexist

### 2018-08-22 paper_simulations.Rmd
time argument to extract abundances

# Compute a data.frame of number of individuals in function of optimal trait
# for competition and growth
landscape_df = function(multiple_traits_scenario, trait_df, trait_weights) {

@@

    population_df = multiple_traits_scenario$compo[,,150] %>%
        as.data.frame() %>%
        rownames_to_column("patch") %>%  # Add patch names as column
        # Transform to tidy data.frame (define name of columns and column name
        # for values)
        gather("species", "N", -patch)

@@

# This function tidy a list of simulation routine to a single data.frame
# suitable to make figures.
tidy_simulation_list = function(simulation_list, set_of_traits, trait_scenarios) {
    simulation_list %>%
        names() %>%
        # Tidy single simulations
        lapply(tidy_simulation,
               given_simul = simulation_list,
               given_traits = set_of_traits,
               given_trait_scenar = trait_scenarios) %>%
        # Re-add names
        set_names(nm = names(simulation_list)) %>%
        # Join into single data.frame
        bind_rows(.id = "scenario") %>%
        # Compute pre-CWMs
        mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .))
}

tidy_simulation = function(scenario, given_simul, given_traits,
                           given_trait_scenar) {
    landscape_df(given_simul[[scenario]], given_traits,
                 trait_scenarios[[scenario]]) %>%
        inner_join(given_traits %>%
                       as.data.frame() %>%
                       rownames_to_column("species"),
                   by = "species") %>%
        group_by(patch) %>%
        mutate(rel_abund = N/sum(N)) %>%
        ungroup()
}
# Initial parameters -----------------------------------------------------------
suppressMessages(devtools::load_all())

@@

# Competition + Dispersion coefficients
A =  0.0005	# Alpha scalar 
d = 0.05 # Dispersal percentage

>>>>

# Compute a data.frame of number of individuals in function of optimal trait
# for competition and growth
landscape_df = function(multiple_traits_scenario, trait_df, trait_weights,
                        time = 150) {

@@

    population_df = multiple_traits_scenario$compo[,,time] %>%
        as.data.frame() %>%
        rownames_to_column("patch") %>%  # Add patch names as column
        # Transform to tidy data.frame (define name of columns and column name
        # for values)
        gather("species", "N", -patch)

@@

# This function tidy a list of simulation routine to a single data.frame
# suitable to make figures.
tidy_simulation_list = function(simulation_list, set_of_traits, trait_scenarios,
                                time = 150) {
    simulation_list %>%
        names() %>%
        # Tidy single simulations
        lapply(tidy_simulation,
               given_simul = simulation_list,
               given_traits = set_of_traits,
               given_trait_scenar = trait_scenarios,
               time = time) %>%
        # Re-add names
        set_names(nm = names(simulation_list)) %>%
        # Join into single data.frame
        bind_rows(.id = "scenario") %>%
        # Compute pre-CWMs
        mutate_at(vars(contains("trait")), funs(cwm = rel_abund * .))
}

tidy_simulation = function(scenario, given_simul, given_traits,
                           given_trait_scenar, time = 150) {
    landscape_df(given_simul[[scenario]], given_traits,
                 trait_scenarios[[scenario]], time = time) %>%
        inner_join(given_traits %>%
                       as.data.frame() %>%
                       rownames_to_column("species"),
                   by = "species") %>%
        group_by(patch) %>%
        mutate(rel_abund = N/sum(N)) %>%
        ungroup()
}
# Initial parameters -----------------------------------------------------------
suppressMessages(devtools::load_all())

@@

# Competition + Dispersion coefficients
A =  0.0005	# Alpha scalar 
d = 0.00 # Dispersal percentage
